Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-12-27 docs/00-manuscripts/ieee/ieee-manuscript.tex
Add geometric, radiometric and atmospheric correction information to appendix F

>>>>

\section{Radiometric, Geometric and Atmospheric correction of hyperspectral data}

The following information was provided externally by the company which was in charge for the image acquisition and preprocessing of the data.

\textbf{Radiometric Correction}

\begin{quote}
The conversion of DNs to spectral radiance was made by using a software designed for the instrument.
Images are originally scaled in 12 bits but they were radiometrically calibrated to 16 bits, reserving the highest value: 65535, for null values.
The procedure was applied on the 23 previously selected images.
Thereafter, the geometric and atmospheric corrections were further applied on them.
\end{quote}

\textbf{Geometric Correction}

\begin{quote}
The aim of this procedure was to reduce the positional errors of the images.
The cartography of reference was GeoEuskadi, UTM, zone 30, datum ETRS-89.
The position was accomplished by coupling an Applanix POS AV 410 system to the sensor, which integrates GPS and IMU systems.
The system provides geographic coordinates of the terrain and relative coordinates of the aircraft (attitude) at each scanned line. Additionally a DSM from GeoEuskadi with a spatial resolution of 1 m was used.
The ortorectified hyperspectral images were compared to orthoimages 1:5000 of GeoEuskadi and the RMSE was calculated, which was below the GSD in the across and along track directions
\end{quote}

\textbf{Atmospheric Correction}

\begin{quote}
The radiance measured by and instrument depends on the illumination geometry and the reflective properties of the observed surface.
Radiation may be absorbed or scattered (Rayleigh and Mie scattering). Scattering is responsible of the adjacency effect, i.e., radiation coming from neighbors areas to the target pixel.
The MODTRAN code was used to modelling the effect of the atmosphere on the radiation.
To represent the aerosols of the study area it was used the rural model, and the optical thickness was estimated on pixels with a high vegetation cover.
Columnar water vapor was estimated by a linear regression ratio where the spectral radiance of each pixel at the band of the maximum water absorption (~906 nm) is compared to its theoretical value in absence of absorption. Nonetheless, this technique is unreliable when a spectral resolution as the one required here is used.
To solve that, a manual selection of the water vapor parameter was made according to the smoothness observed on the reflectance peak at 960 nm.
The mid-latitude summer atmosphere model was also used.
The output of this procedure was reflectance from the target pixel scaled between 0 and 10,000.
\end{quote}

\textbf{Acquisition days}

\begin{quote}
The image acquisitions were originally attempted during one day (29) but due to the variable meteorological conditions some stands had to be imaged the next day.
\end{quote}
